---
title: "Reproducible Pitch"
author: "Ashish Veera"
date: "11/29/2017"
output: ioslides_presentation
---


## Introduction
This presentation contains documentation for the Diamond price prediction application. The application can be found through the below mentioned link 
https://ashishveera.shinyapps.io/MyApp/


## Fucntionality of the application
This application is building a linear regression model using `diamonds` data set and is predicting the price of a diamond depending on its properties.The application allows the user to select:
- Carat 
- Cut 
- Color 
- Clarity 

Finally, builds a plot and gives predicted price of the diamond.

## Data used

The data used for this application is `diamonds` data set, which is part of `ggplot2` package.
This data set contains the information about 53940 diamonds with 10 variables:
```{r echo=FALSE}
library(ggplot2)
```

```{r echo=FALSE}
summary(diamonds)

```

## Shiny files

The application is built using Shiny package and the source code is in 2 files:
- `ui.R`
- `server.R`

These files can be found here:

https://github.com/AshishVeera/Course-Project-Shiny-Application-and-Reproducible-Pitch/blob/master/ui.R

https://github.com/AshishVeera/Course-Project-Shiny-Application-and-Reproducible-Pitch/blob/master/server.R


